Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-03 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
organized analysis/paper dir

```{r, scatter-{{hot_chr}}}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == {{keller_mediator}}, nonlocal = nonlocal_symbol, local = local_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", {{hot_chr}}, "_scatter.svg")
fnpdf <- paste0("Chr", {{hot_chr}}, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
plotly::ggplotly(p)
```

@@

```{r, scols-{{hot_chr}}}
scols1 <- 1L + (rownames(pm) %in% local_annot2$symbol)
scols2 <- rownames(pm) %in% (med_tib %>% filter(local_symbol == {{keller_mediator}}, lod_diff > 1.5))$nonlocal_symbol
```

@@

```{r, index_v_position-{{hot_chr}}}
bar <- foo %>%
  filter(local_symbol == {{keller_mediator}})

>>>>

```{r, scatter-{{hot_chr}}}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == "{{keller_mediator}}", nonlocal = nonlocal_symbol, local = local_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", {{hot_chr}}, "_scatter.svg")
fnpdf <- paste0("Chr", {{hot_chr}}, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
plotly::ggplotly(p)
```

@@

```{r, scols-{{hot_chr}}}
scols1 <- 1L + (rownames(pm) %in% local_annot2$symbol)
scols2 <- rownames(pm) %in% (med_tib %>% filter(local_symbol == "{{keller_mediator}}", lod_diff > 1.5))$nonlocal_symbol
```

@@

```{r, index_v_position-{{hot_chr}}}
bar <- foo %>%
  filter(local_symbol == "{{keller_mediator}}")
